NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-03-30 paper/paper_entailVis.tex
update section 6.4
update figures
update teaser

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
% \vspace{-8mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 % \vspace{-3mm}
  \caption{
The interface of the NLIZE system. During exploration, we can filter through a large number of sentence examples summarized in (A) and select examples of interest displayed in (B). The model internal information (attention) is displayed in (D) and (E). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (F). Finally, the high-level model structure and the updates to the model are summarized in (C).
}
\label{fig:teaser}
}

>>>>

%make paper compact
\setlength{\parskip}{0.04cm}
\setlength{\parindent}{0.7em}

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
\vspace{-4mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 \vspace{-4mm}
  \caption{
The interface of the NLIZE system. During exploration, we can filter through a large number of sentence pairs summarized in (a) and the current selected pair is displayed in (b). The model internal information (attention) is displayed in (d) and (e). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (f). Finally, the high-level model structure and the updates to the model are summarized in (c).
}
% \vspace{-2mm}
\label{fig:teaser}
}

### 2018-03-30 paper/relatedWorks.tex
space squeeze
update teaser

\textbf{Visualization Of NLP Models.}
Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studys have been dedicated to neural language processing models.
%
The previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models but also revealed enormous possibility for future applications.
% There is many unresolved challenges and the
The early work on character-level recurrent networks~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text. The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models is examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al. ~\cite{LiChenHovy2015}.
In the RNNVis~\cite{MingCaoZhang2017} work, Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
The RNNbow~\cite{CashmanPattersonMosca2017} system helps domain experts understand how the model is trained by visualizing the backpropagation gradient information.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
%As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting.

All the previously discussed works either focus on the training process or examine the trained model as a fixed object. In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.
%In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on

>>>>

\textbf{Visualization of NLP Models.}
Compared to the multitude of research for making sense of convolutional neural networks, relatively fewer studys have been dedicated to neural language processing models.
%
The previous works~\cite{KarpathyJohnson2015, LiChenHovy2015, StrobeltGehrmannPfister2018, LiuBremerJayaraman2018} not only demonstrated the benefit of visualization in understanding NLP models but also revealed enormous possibility for future applications.
% There is many unresolved challenges and the
The early work on character-level recurrent networks~\cite{KarpathyJohnson2015} demonstrates the effectiveness of the hidden state in capturing the unique pattern in the training text. The compositionality (i.e., build the meaning of a sentence from the meaning of words and phrases) exhibited in neural network linguistic models is examined by utilizing techniques inspired by model interpretability techniques in computer vision by Li et al. ~\cite{LiChenHovy2015}.
In the RNNVis~\cite{MingCaoZhang2017} work, Ming et al. visualize the hidden state units in a recurrent neural network based on their expected responses to model input.
The RNNbow~\cite{CashmanPattersonMosca2017} system helps domain experts understand how the model is trained by visualizing the backpropagation gradient information.
The LSTMvis~\cite{StrobeltGehrmannPfister2018} work employs a line plot style visual encoding to represent the time varying hidden states of the recurrent neural network. The word embedding visualization work~\cite{LiuBremerJayaraman2018} illustrates how semantic relationship can be recovered by linear projections in the high-dimensional word embedding space (e.g., word2vec~\cite{MikolovSutskeverChen2013} or Glove~\cite{PenningtonSocherManning2014}).
%As discussed in the introduction, the experts guided exploration calls for the ability to interact with internal of the model in a dynamic setting. 
%
All the previously discussed NLP model visualization works either focus on the training process or examine the trained model as a fixed object. In contrast, the proposed method allows direct user interaction with the internals of the trained model in a dynamic environment, which enables unrestrictive exploratory analysis that is not possible before.
%In addition, instead of exploring a language model or low-level, the proposed method focus on a specific NLP task, which provide insight on
